Utilizing Machine Learning to Accelerate Automated Assignment of Backbone NMR Data

### 2015-04-04 Papers_and_Presentations/paper_spring_2015/paper.tex
Another update
Yet another paper update

\indent In step 5, the algorithm selects the assignment with the lowest cost to continue the search process. A solution is reached when all tiles have been placed in an assignment. If the assignment is not a solution, the amino acid type of the next residue in the protein sequence is retrieved. Any unplaced tile that corresponds to that amino acid type with a confidence level above the threshold is placed at the next location in the sequence. In the special case that the next amino acid type is proline, only the special proline tiles are considered for placement. The cost is then adjusted to include the newly placed tile. Step 5 is repeated until a solution has been reached.

@@

\noindent Rachel Davis is currently on the path to obtaining a B.S. in both Computer Science and Mathematics. This is the second year conducting this sequencing research. Her research includes not only this primary structuring of proteins, but also a collaborative tertiary structuring algorithm. Currently she is applying to summer internships closely relating to both her interests and expertise.

\noindent Katie Roth is pursuing a B.A. in Mathematics and Computer Science. She has been working on this research for two years, and enjoys it immensely. Katie is the treasurer of the Women in Mathematics and Computer Science and an active member of Math Club. She is currently applying for summer research experiences, as well as internships.

>>>>

\indent In step 5, the algorithm selects the assignment with the lowest cost to continue the search process. The solution is reached when all tiles have been placed in an assignment and the solution has the lowest cost. If the assignment is not a solution, the amino acid type of the next residue in the protein sequence is retrieved. Any unplaced tile that corresponds to that amino acid type with a confidence level above the threshold is placed at the next location in the sequence. In the special case that the next amino acid type is proline, only the special proline tiles are considered for placement. The cost is then adjusted to include the newly placed tile. Step 5 is repeated until a solution has been reached.

@@

\noindent Rachel Davis is currently on the path to obtaining a B.S. in both Computer Science and Mathematics, with a minor in Data Analytics. This is the second year conducting this sequencing research. Her research includes not only this primary structuring of proteins, but also a collaborative tertiary structuring algorithm. For this coming summer, she is researching at East Carolina University working on Software Testing.

\noindent Katie Roth is pursuing a B.A. in Mathematics and Computer Science. She has been working on this research for two years, and enjoys it immensely. Katie is the treasurer of the Women in Mathematics and Computer Science and an active member of Math Club. She will be gracing the University of Michigan with her researching talents working on a Big Data learning cooperative.
